% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\usepackage{hyperref}
\usepackage{geometry}


\def\name{Gao Zhiyuan}
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Computer Science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.9in, 9.0in},
  left=0.8in,
  top=0.70in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}
% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0.6em}
    \setlength{\textwidth}{7.5in}
    \setlength{\topmargin}{-0.6in}
    \setlength{\textheight}{19.5in}
  }
}{
  \end{list}
}

%\setlength{\voffset}{0.1in}
%\setlength{\paperwidth}{8.5in}
%\setlength{\paperheight}{15in}%11in
%\setlength{\headheight}{0in}
%\setlength{\headsep}{0in}
%\setlength{\textheight}{15in}
%\setlength{\textheight}{19.5in}% distance between end of line and end of page
%\setlength{\topmargin}{-0.6in}
%\setlength{\textwidth}{7.6in}
%\setlength{\topskip}{0in}
%\setlength{\oddsidemargin}{-0.5in}
%\setlength{\evensidemargin}{-0.24in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in

%\pagestyle{empty}
%\raggedbottom
%\raggedright
%\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtiny}[1]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtinytwo}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance


%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Gao Zhiyuan}  & +86 13262224615\\
\  &  alapha23@gmail.com
\end{tabular*}\vspace{-9.0pt}
\\

\vspace{0.03in}


\resheading{Work Experiences}
\begin{itemize}
\item
	\ressubheading{Amazon Web Services}{}{Associate Solutions Architect}{Jun. 2024 - now}
	\begin{itemize}
		\resitem{
1. Global Network Infrastructure Optimization Project\\
- Monitored and analyzed network latency between the USA and Singapore, identifying bottlenecks within individual CloudFront components causing TCP reconnections.\\
- Developed and implemented a PoP warm-up strategy and an NGINX-based solution to ensure persistent TCP connections.\\
- Reduced cross-region latency inconsistency from 60\% to under 10\%.\\
		}
		\resitem{
2. RAG-based Chatbot for AWS Knowledge\\
- A chatbot using Retrieval Augmented Generation, to answer technical questions specifically focused on AWS services \\
- Evaluate the responses in terms of hallucination, self-knowledge dependence, Context Utilization and etc. \\
- The tech stack includes AWS Lambda, RDS, Opensearch, Bedrock/Claude, Sagemaker, Rerank.\\
		}
		\resitem{
3. Multimodal Content Guardrailing\\
- Employed a model unlearning project to \"forget\" certain concepts during inference time\\
- Moderate Content through AWS Nova, Bedrock Guardrails, and the model unlearning project \\
		}
		\resitem{
4. Client Security Incident Response\\
- Managed customer security incidents through advanced attack behavior analysis, device fingerprint profiling, and cloud attack path mapping. \\
- Enhanced client cloud security by designing and implementing robust security architectures and strategies. \\
		}
	\end{itemize}

	\ressubheading{Trilogy}{}{Software Engineer}{Aug. 2022 - Aug. 2023}
	\begin{itemize}
		\resitem{
1. AWS Cost Optimization project\\
- Lowered AWS Service Costsfrom ~25 million USD annually down to ~5 million USD in a team of 3. \\
- Designed non-intrusive, sustainable plans to guarantee resource sharing, user resource awareness, automated anomaly detection and permission rules. \\
		}
		\resitem{
2. Social Platform for Education\\
A social platform that enables 4-12 grade students to memorize curricular knowledge through making posts with the help of AI and memorization techniques.\\
The tech stack includes Next.js, Prisma/MySQL, GPT-3, Stable-Diffusion, Docker and AWS Devops.\\
		}
		\resitem{
3. Data Platform based on Azure AD\\
Construct a graph-based data platform and use it to calculate company employee interaction intensity.\\
Extract data from MS 365 through Azure Graph API, engineer the data into graph relationships and maintain the in the graph database.\\
		}
		\resitem{
4. Automate Company ERP operations on NetSuite\\
In charge of project ideation, development and delivery and was solely responsible for communication with the clients. Tech stack involves Selenium, Chrome Plugin, Python and Javascript\\
		}
	\end{itemize}
	\ressubheading{MISE}{}{Devops Engineer}{Jun. 2022 - Sep. 2022}
	\begin{itemize}
		\resitem{
Addressed latency spikes in an AWS Lambda-based startup application during peak traffic hours.\\
Diagnosed and resolved performance bottlenecks by analyzing AWS Lambda, API Gateway, and MySQL RDS.\\
Streamlined deployment processes using Terraform Infrastructure as Code (IaC).\\
			}
	\end{itemize}
\end{itemize}


\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{Seoul National University}{City Energy Lab}{Research Intern}{Sep. 2023 - Now.}
		\begin{itemize}
		\resitem{
RAG-based Chatbot for Urban Planning\\
- Built a RAG chatbot with FAISS, parent-child chunking, keyword-extration for domain-specific knowledge\\
- Designed a chatbot with NextJS, Typescript, Prisma, FAISS and OpenAI API \\
		}
	\end{itemize}
	
	\ressubheadingtiny{Seoul National University}{}{2019}
	\begin{itemize}
		\resitem{
Project Name: Accomodate Input Spikes with AWS Lambda Functions\\
			A hyrbid system of Dockers and AWS Lambda Functions, where stable workloads are running on docker and input rate spikes are offloaded to AWS Lambda Functions, \\
			Implemented job scheduling/balancing algorithm to coordinate Lambda Functions' life cycle, data relay, and system-level dynamic scaling }
	\end{itemize}
\item
	\ressubheading{Google}{Summer of Code}{Apache Foundation}{2019}
	\begin{itemize}
		\resitem{Engineered Apache Nemo to process single-stage batch data with AWS Lambda Functions}
	\end{itemize}
\item
	\ressubheading{Chinese Academy of Science}{PLCT Lab}{QEMU Researcher}{2020}
	\begin{itemize}
		\resitem{One patch to QEMU upstream to emulate Nuclei RISC-V SoCs with customised interrupt controllers and registers, \\
			Delivered an oral presentation at CRVA 2020}
	\end{itemize}

\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{National Cheng Kung University}{Taiwan}{B.S., Political Science}{Sep. 2015 - May. 2017}
\item
	\ressubheading{Seoul National University}{Korea}{B.S., Computer Science and Engineering}{Sep. 2019 - Aug. 2024}
\end{itemize}

\begin{description}
\item[Skills:]
Languages: Python, Java, Typescript, C/C++ \\
Backend Development: NextJS, Typescript, Prisma, MySQL \\
DevOps: AWS, Redis, K8S, Docker  \\
Others: AI Agent / RAG development, Serverless development, QEMU, React, Selenium  \\
\item[Languages:]
Chinese, English (TOEFL 100), Japanese (JLPT N1) and Korean
\end{description}

%\resheading{Misc}
\end{document}
