% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7.3in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.24in}
\setlength{\evensidemargin}{-0.24in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Gao Zhiyuan}  & +86 13262224615\\
\  &  alapha23@gmail.com \\
\end{tabular*}
\\

\vspace{0.05in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{National Cheng Kung University}{Taiwan}{B.S., Engineering Science}{Sep. 2015 - May. 2017}
	\begin{itemize}
		\resitem{Relevant courses: Signals and Sysytems, Logic Design, Electronics, etc.}
	\end{itemize}

\item
	\ressubheading{Seoul National University}{Korea}{Exchange Student, Computer Science and Engineering}{Sep. 2017 - Jul. 2018}
	\begin{itemize}
		\resitem{Relevant courses: Operating System, System Programming, Computer Architecture, Compiler, Computer Vision, etc.}
	\end{itemize}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{SUSE}{Beijing, China}{Intern}{Oct. 2018 - Jan. 2019}
	\begin{itemize}
		\resitem{Part of a group working for openSUSE Tumbleweed testing}
		\resitem{Programming Perl on openQA.}
	\end{itemize}

\item 
	\ressubheading{DYSK Labs}{Taiwan}{Intern}{Aug. 2018 - Sep. 2018}
	\begin{itemize}
		\resitem{Setup GPU/CPU unified memory for tensorflow on ppc64le, learnt tensorflow memory allocator from source code on my own}
		\resitem{Tested tensorflow build on ppc64le with custom tests.}
		\resitem{Wrote documentation for programmers describing the environment.}
	\end{itemize}

\end{itemize}

\resheading{School Projects}
\begin{itemize}
\item
	\ressubheading{SnuPl/1 compiler}{}{Compiler Course, 4190.409}{Sep. 2017 - Jan. 2018}
	\begin{itemize}
		\resitem{Programmed and debugged full frontend of the compiler.}
		\resitem{Implemented compiler code generator for x86 assembly.}
	\end{itemize}
\item
	\ressubheading{Source Code Plagiarism Detector}{}{}{Jan. 2018 - Feb. 2019}
	\begin{itemize}
		\resitem{Designed and implemented source code plagiarism detector,}
		\resitem{Visualized plagiarism results with graphviz and Neo4j.}
	\end{itemize}


\item
	\ressubheading{Weighted Round Robin Scheduler}{}{Operating System Course, 4190.307}{Mar. 2018 - Jul. 2018}
	\begin{itemize}
		\resitem{Worked on the WRR Scheduler(Weighted Round Robin) project in a team of three.}
		\resitem{Programmed and debugged WRR algorithm into linux kernel on Samsung Artik device. Learnt linux kernel programming on my own}
		\resitem{Designed load-balancing between 8 cores.}
		\resitem{Tested the project with plenty of test cases.}
	\end{itemize}

\item
	\ressubheading{Other Projects}{}{}{2015 - 2018}
	\begin{itemize}
		\resitem{Added features to AMACC\(Another Mini ARM C Compiler\) A Small C Compiler generating ELF executable for Arm architecture}
		\resitem{Deploy tiny-yolov3 and darknet on Raspberry Pi, fine-tune tiny-yolov3 with WIDER FACE dataset}
		\resitem{Built a fecal sampler on Raspberry Pi, designed power supply for actuator controlling.}
	\end{itemize}

\end{itemize}


\resheading{Skills}

\begin{description}
\item[Programming Languages:]
C/C++, Java and x86 Assembly
\item[Natural Lanuages:]
Native speaker in Chinese, Proficient in English(TOEFL 100) and Japanese(JLPT N1)
\item[Miscellaneous:]
Software configuration management, strong verbal and written communication skills, troubleshooting and debugging skills, good teams skills
\end{description}

\end{document}
