% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\usepackage{hyperref}
\usepackage{geometry}


\def\name{Gao Zhiyuan}
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Computer Science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.9in, 9.0in},
  left=0.8in,
  top=0.70in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}
% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0.6em}
    \setlength{\textwidth}{7.5in}
    \setlength{\topmargin}{-0.6in}
    \setlength{\textheight}{19.5in}
  }
}{
  \end{list}
}

%\setlength{\voffset}{0.1in}
%\setlength{\paperwidth}{8.5in}
%\setlength{\paperheight}{15in}%11in
%\setlength{\headheight}{0in}
%\setlength{\headsep}{0in}
%\setlength{\textheight}{15in}
%\setlength{\textheight}{19.5in}% distance between end of line and end of page
%\setlength{\topmargin}{-0.6in}
%\setlength{\textwidth}{7.6in}
%\setlength{\topskip}{0in}
%\setlength{\oddsidemargin}{-0.5in}
%\setlength{\evensidemargin}{-0.24in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in

%\pagestyle{empty}
%\raggedbottom
%\raggedright
%\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtiny}[1]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtinytwo}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance


%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Gao Zhiyuan}  & +82 1072198956\\
\  &  alapha23@gmail.com
\end{tabular*}\vspace{-9.0pt}
\\

\vspace{0.03in}


\resheading{Work Experiences}
\begin{itemize}
\item
	\ressubheading{Trilogy}{}{Software Engineer}{Aug. 2022 - Now}
	\begin{itemize}
		\resitem{
1. AWS Cost Optimization project\\
- Lowered AWS Service Costsfrom ~25 million USD annually down to ~5 million USD in a team of 3. \\
- Designed non-intrusive, sustainable plans to guarantee resource sharing, user resource awareness, automated anomaly detection and permission rules. \\
		}
		\resitem{
2. Social Platform for Education\\
A social platform that enables 4~12 grade students to memorize curricular knowledge through making posts with the help of AI and memorization techniques.\\
The tech stack includes Next.js, Prisma/MySQL, GPT-3, Stable-Diffusion, Docker and AWS Devops.\\
		}
		\resitem{
3. Data Platform based on Azure AD\\
Construct a graph-based data platform and use it to calculate company employee interaction intensity.\\
Extract data from MS 365 through Azure Graph API, engineer the data into graph relationships and maintain the in the graph database.\\
		}
	\end{itemize}
	\ressubheading{MISE}{}{Devops Engineer}{Jun. 2022 - Sep. 2022}
	\begin{itemize}
		\resitem{
			- Solve system performance bottleneck by analysing AWS Lambda, API Gateway and MySQL RDS \\
			- Apply Terraform IaaS for fast deployment \\
			- Enabled development environment vs. production environment split to stablise our services\\
			- Lead the team to learn to apply Github Best practices (PRs, code reviews) \\
			- Implement the development/staging/release processes of our product \\
			}
	\end{itemize}
	\ressubheading{MetaMUI-SovereignWallet}{}{Python SDK Developer}{Dec. 2021 - Mar. 2022}
	\begin{itemize}
		\resitem{Migrate Rust SDK to Python SDK for MetaMUI blockchain built with Substrate framework}
	\end{itemize}
        \ressubheading{Alibaba Cloud}{}{Intern for Summer of Code}{Jun. 2021 - Sep. 2021}
        \begin{itemize}
                \resitem{Nodejs Dev/QA intern for Serverless Devs. Developed unit tests, integration tests, and APIs and Git workflow automation with Typescript, Jest and Github workflow}
        \end{itemize}
\item
	\ressubheading{Chinese Academy of Science}{PLCT Lab}{QEMU Researcher}{May. 2020 - Nov. 2020}
	\begin{itemize}
		\resitem{One patch to QEMU upstream to emulate Nuclei RISC-V SoCs with customised interrupt controllers and registers, \\
			Delivered an oral presentation at CRVA 2020}
	\end{itemize}
\item
	\ressubheading{Google}{Summer of Code}{Java Intern}{Jun. 2019 - Sep. 2019}
	\begin{itemize}
		\resitem{Engineered Apache Nemo to process single-stage batch data with AWS Lambda Functions}
	\end{itemize}
\item
	\ressubheading{Seoul National University}{Software Platform Lab}{Research Intern}{Mar. 2019 - Nov. 2019}
	\begin{itemize}
		\resitem{Enable distributed dataflow system to benefit from serverless computing using AWS Lambda Functions, Java and Apache Nemo \\
			Two published domestic papers, and one pending research for international conferences}
	\end{itemize}
\item
	\ressubheading{SUSE}{Beijing, China}{QA Intern}{Oct. 2018 - Jan. 2019}
	\begin{itemize}
			\resitem{Part of the Dev\&QA team working on openSUSE and SUSE Linux Enterprise, with git, openQA and perl}
	\end{itemize}

\end{itemize}


\resheading{Research Project}
\begin{itemize}
\item
	\ressubheadingtiny{Accomodate Input Spikes with AWS Lambda Functions}
	\begin{itemize}
		\resitem{
			A hyrbid system of Dockers and AWS Lambda Functions, where stable workloads are running on docker and input rate spikes are offloaded to AWS Lambda Functions, \\
			Implemented job scheduling/balancing algorithm to coordinate Lambda Functions' life cycle, data relay, and system-level dynamic scaling }
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{National Cheng Kung University}{Taiwan}{B.S., Political Science}{Sep. 2015 - May. 2017}
\item
	\ressubheading{Seoul National University}{Korea}{B.S., Computer Science and Engineering}{Sep. 2019 - )}
\end{itemize}

\begin{description}
\item[Skills:]
Languages: Python, Java, Typescript, C/C++
Backend Development: Typescript, Prisma, MySQL
Devops: AWS, Redis, K8S, Docker, Azure AD Graph APIs, CI/CD
Others: Serverless development, QEMU, React, GPT-3, Stable Diffusion
\item[Languages:]
Chinese, English (TOEFL 100), Japanese (JLPT N1) and Korean
\end{description}

%\resheading{Misc}
\end{document}
