% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\usepackage{hyperref}
\usepackage{geometry}


\def\name{Gao Zhiyuan}
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Computer Science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.9in, 9.0in},
  left=0.8in,
  top=0.70in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}
% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0.6em}
    \setlength{\textwidth}{7.5in}
    \setlength{\topmargin}{-0.6in}
    \setlength{\textheight}{19.5in}
  }
}{
  \end{list}
}

%\setlength{\voffset}{0.1in}
%\setlength{\paperwidth}{8.5in}
%\setlength{\paperheight}{15in}%11in
%\setlength{\headheight}{0in}
%\setlength{\headsep}{0in}
%\setlength{\textheight}{15in}
%\setlength{\textheight}{19.5in}% distance between end of line and end of page
%\setlength{\topmargin}{-0.6in}
%\setlength{\textwidth}{7.6in}
%\setlength{\topskip}{0in}
%\setlength{\oddsidemargin}{-0.5in}
%\setlength{\evensidemargin}{-0.24in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in

%\pagestyle{empty}
%\raggedbottom
%\raggedright
%\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtiny}[1]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtinytwo}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance


%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Gao Zhiyuan}  & +86 13262224615, +852 52140290\\
\  &  alapha23@gmail.com
\end{tabular*}\vspace{-9.0pt}
\\

\resheading{Summary}
Infrastructure \& Cloud Support Engineer specialising in AWS availability, incident response, and performance tuning. 4+ years troubleshooting complex production issues across EC2, VPC, S3, EKS and serverless stacks for high‑traffic enterprises. Adept at reproducing hard‑to‑trace errors, performing root‑cause analysis, and automating fixes with Terraform/CloudFormation \& Python/Bash. Proven record of cutting latency 60\% $\rightarrow$ 10\% and AWS spend \$25M $\rightarrow$ \$5M while ensuring secure, compliant operations. Thrive in fast‑moving, multicultural teams and communicate technical findings clearly to engineers and business stakeholders.

\resheading{Core Competencies}
\textbf{AWS Infrastructure:} EC2, S3, VPC, IAM, CloudWatch, CloudFront, Lambda, RDS, EKS/ECS\\
\textbf{Troubleshooting\&Ops:} Incident triage, MTTR reduction, log‑driven RCA, cost optimisation\\
\textbf{IaC\&Automation:} Terraform, AWS CDK/CloudFormation, Ansible, CI/CD (GitHub Actions)\\
\textbf{Scripting\&Languages:} Python, Bash, Go (basic) – build diagnostic tooling \& remediation scripts\\
\textbf{Containers\&OS:} Docker, Kubernetes, Linux (Debian/Alpine/CentOS), Server administration\\
\textbf{Observability:} Prometheus/Grafana, CloudWatch Logs \& Metrics, X‑Ray, ELK stack\\
\textbf{Soft Skills:} Customer‑facing support, cross‑team collaboration, documentation\\

\resheading{Work Experiences}
\begin{itemize}
\item
	\ressubheading{Amazon Web Services}{}{Associate Solutions Architect}{Jun. 2024 - now}
	\begin{itemize}
		\resitem{
1. Resolved cross‑region latency spikes for a global e‑commerce client by analysing CloudFront TCP reset patterns, designing\& deploying an NGINX keep‑alive solution; cut inconsistent RTT from 60\% to 10\% with zero downtime.
                }
		\resitem{
2. Automated EKS unmanaged→managed node‑group migration with a Python user‑data checker, slashing manual effort 80\% and avoiding extended‑support fees.
		}
		\resitem{
3. Improve Yolov8 Inference Throughput by 185\% \\
- Using Pytorch to convert the model weight of Yolov8 for AWS Inf1 Instance. \\
- Gained 1.85x throughput increase whilst lowering the cost down to 25\%.  
                }
	\end{itemize}

	\ressubheading{Trilogy}{}{Software Engineer}{Aug. 2022 - Aug. 2023}
	\begin{itemize}
		\resitem{
1. Led company‑wide AWS cost‑optimisation initiative: built automated right‑sizing scripts (Python+AWS SDK), introduced multi-tenancy, resource‑ownership tagging and anomaly detection → annual spend \$25 M $\rightarrow$ \$5M.
		}
		\resitem{
2. Deployed Terraform modules \& Jenkins pipelines to standardise VPC \& IAM baselines across 15 accounts, shrinking mean provisioning time from 3 days to 4 hours.\\
		}
	\end{itemize}
	\ressubheading{MISE}{}{Devops Engineer (Contract)}{Jan. 2022 - Sep. 2022}
	\begin{itemize}
		\resitem{
Investigated and fixed Lambda cold‑start latency spikes during traffic surges; tuned memory/timeout and introduced provisioned concurrency $\rightarrow$ p95 response time ‑40\%\\
			}
		\resitem{
Hardened API Gateway + WAF configuration, blocking OWASP top‑10 vectors; documented remediation steps for support runbooks.\\
			}
	\end{itemize}
	\ressubheading{MetaMUI-SovereignWallet}{}{Python SDK Engineer}{Jun. 2021 - Jan. 2022}
	\begin{itemize}
		\resitem{
Ported Rust blockchain SDK to Python, writing integration tests to replicate consensus edge cases; accelerated developer onboarding 3×.\\
			}
	\end{itemize}
\end{itemize}


\resheading{Projects}
\begin{itemize}
\item
	\ressubheadingtiny{Seoul National University}{}{2019}
	\begin{itemize}
		\resitem{
Project Name: Accomodate Input Spikes with AWS Lambda Functions\\
			A hyrbid system of Dockers and AWS Lambda Functions, where stable workloads are running on docker and input rate spikes are offloaded to AWS Lambda Functions, \\
			Implemented job scheduling/balancing algorithm to coordinate Lambda Functions' life cycle, data relay, and system-level dynamic scaling }
	\end{itemize}
\item
	\ressubheading{Google}{Summer of Code}{Apache Foundation}{2019}
	\begin{itemize}
		\resitem{Engineered Apache Nemo to process single-stage batch data with AWS Lambda Functions}
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{National Cheng Kung University}{Taiwan}{Engineering Science}{Sep. 2015 - May. 2017}
\item
	\ressubheading{Seoul National University}{Korea}{B.S., Computer Science and Engineering}{Sep. 2019 - Aug. 2024}
\end{itemize}

\begin{description}
\item[Tech Stack Snapshot]
AWS • Terraform • CloudFormation / CDK • Python\&Bash • Linux \&Windows Admin • Docker/Kubernetes • GitHub Actions • Prometheus/Grafana • Ansible • Jira / Agile Scrum
\item[Languages:]
Chinese, English (TOEFL 100), Japanese (JLPT N1) and Korean
\end{description}

%\resheading{Misc}
\end{document}
