% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Gao Zhiyuan}  & Programming Portfolio\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Projects}
\begin{itemize}
\item	
	\begin{itemize}{\textbf{Round Robin Scheduler for Multicore System}}
			\resitem{}
		\resitem{Implemented round robin algorithms in Linux kernel, replaced CFS scheduler of Linux kernl.}
		\resitem{Implemented load balancing between eight cores and tested on Artik10 board.}
	\end{itemize}


\item 
	\begin{itemize}{\textbf{SNU Source Code Plagiarism Detector}}
		\resitem{}
		\resitem{Wrote a tool that turns GCC parse trees into abstract syntax trees}
		\resitem{Compare different abstract syntax trees according to Tree Edit Distance algorithm}
		\resitem{Designed and tested an equation that draws conformance rate based on all compared scopes}
		\resitem{Visualized conformance by Graphviz and Neo4j}
	\end{itemize}
		

\item
	\begin{itemize}{\textbf{Software Refactor SURFEX and UWG}}
		\resitem{}
		\resitem{Migrate UWG modules into SURFEX software.}			
		\resitem{Constructed automatic test program to verify correctness of the merged software}
		\resitem{Programmed windows powershell scripts to enable automatical installation and configuration.}
	\end{itemize}



\item
	\begin{itemize}{\textbf{SnuPL/1 Compiler}}
		\resitem{}
		\resitem{Developed scanner, parser, semantics checker and code generator.}
		\resitem{Compiled into intel x86 assembly instructions}
		\resitem{Tested and debugged all components against SnuPL/1 code set.}
	\end{itemize}



\item
	\begin{itemize}{\textbf{Geo-tagged Filesystem based on EXT2}}
		\resitem{}
		\resitem{Designed a new filesystem which grants permission only when location condition matches.}
		\resitem{Characterized inode of EXT2 and add gps information at every file creation and modification.}
		\resitem{Characterized e2fsprogs ext2 utilities and tested the filesystem on Samsung Artik10.}
	\end{itemize}



\item
	\begin{itemize}{\textbf{Embed tiny-yolo on Raspberry Pi for Face Detection}}
		\resitem{}
		\resitem{Train tiny-yolov3 with WIDER-Face dataset on darknet.}
		\resitem{Migrated and charactized darknet onto Raspberry Pi}
	\end{itemize}

\item
	\begin{itemize}{\textbf{Rotation Based Read-write Lock}}
		\resitem{}
		\resitem{Designed a new synchronization mechanism relating to rotation information of the device.}
		\resitem{Constructed two circular lists keeping information of waiting readers and writers.}
		\resitem{Tested the mechanism on Samsung Artik10.}
	\end{itemize}


\item
	\begin{itemize}{\textbf{Crop monitoring system with STM32 Data Collection}}
			\resitem{}
		\resitem{Set up RTOS web server on STM32 to broadcast collected data.}
		\resitem{Programmed STM32 to activate and control sensors including DHT11 and yl69.}
	\end{itemize}

\end{itemize}

\end{document}
