% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{15in}%11in
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{15in}
\setlength{\textheight}{19.5in}% distance between end of line and end of page
\setlength{\topmargin}{-0.6in}
\setlength{\textwidth}{7.6in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.24in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtiny}[1]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance
\newcommand{\ressubheadingtinytwo}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-8.5pt}} %this one alters line distance


%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Gao Zhiyuan}  & +86 13262224615\\
\  &  alapha23@gmail.com
\end{tabular*}
\\

\vspace{0.03in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{National Cheng Kung University}{Taiwan}{B.S., Engineering Science}{Sep. 2015 - May. 2017}
\item
	\ressubheading{Seoul National University}{Korea}{Undergraduate, Computer Science and Engineering}{Sep. 2017 - ongoing}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Software Platform Lab}{Seoul National University}{Intern}{Mar. 2019 - ongoing}
	\begin{itemize}
		\resitem{Part of a group working on distributed dataflow system -- Nemo, an Apache Incubator project}
	\end{itemize}
\item
	\ressubheading{SUSE}{Beijing, China}{Intern}{Oct. 2018 - Jan. 2019}
	\begin{itemize}
		\resitem{Part of the QA team working on openSUSE and SUSE Linux Enterprise}
		\resitem{Add QA test cases with Perl Programming on openQA, with test cases version control and bug follow-ups}
	\end{itemize}
\end{itemize}

\resheading{Publications}
\begin{itemize}
\item
	\ressubheading{Serverless Computing: Pitfalls and Solutions}{}{Korean Computer Congress 2019}{First Author}
\item
	\ressubheading{Lambda Executor: extend Apache Nemo with serverless functions}{}{Korean Software Congress 2019}{First Author}
\item
	\ressubheadingtiny{A third-author paper rejected by EuroSys 2020}
	\begin{itemize}
		\resitem{A hyrbid system for dealing with bursty input rates in stream processing applications, which dynamically creates VMs and serverless containers.}
		\resitem{Actively participated in paper writing, research experiments and evaluation, algorithm design regarding VM scaling, and engineering the dataflow framework.}
	\end{itemize}
\end{itemize}

\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{Incubator-nemo Lambda Executor}{Apache Software Foundation}{Google Summer of Code}{May. 2019 - Sep. 2019}
	\begin{itemize}
		\resitem{Migrated executor for batch applications to AWS Lambda functions.}
		\resitem{Enabled executor on lambda functions' lifecycle management. Project only tested on single-stage stateless applications.}
	\end{itemize}
\item
	\ressubheadingtinytwo{SnuPl/1 compiler}{Sep. 2017 - Jan. 2018}%{}{Compiler Course, 4190.409}{Sep. 2017 - Jan. 2018}
	\begin{itemize}
		\resitem{Programmed and debugged full frontend of the compiler.}
		\resitem{Implemented compiler code generator for x86 assembly.}
	\end{itemize}
\item
	\ressubheadingtinytwo{Weighted Round Robin Scheduler}{Mar. 2018 - Jul. 2018}%{}{Operating System Course, 4190.307}{Mar. 2018 - Jul. 2018}
	\begin{itemize}
		\resitem{Worked on the WRR Scheduler(Weighted Round Robin) project in a team of three.}
		\resitem{Programmed and debugged WRR algorithm into linux kernel on Samsung Artik device, with load-balancing between 8 cores.}
	\end{itemize}
\end{itemize}

\end{document}
